SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-01-25 scipy-1.0/paper.tex
Move roadmap into Future Work subsection

\subsection*{Roadmap}

@@

\subsection*{Future development}

Future development plans include a major rewrite of the \texttt{scipy.sparse}
module, which is already underway\cite{abbasi2018sparse}. This is due to the
current interface only supporting two-dimensional objects. Even sub-arrays are
two-dimensional, and dimensions greater than two aren't supported. The new
package supports dimensions greater than two, and it bases itself around arrays
rather than matrices (which is strictly more powerful). It also features
improved inter-operability with NumPy and other community packages.

\fixme{This section should include key issues: sparse arrays, ndimage pixel vs
point, splines, fftpack vs. np.fft and linalg vs. np.linalg, under-maintained
submodules.}

>>>>

\subsection*{Future Work}

@@
